\documentclass[12pt]{article}

\usepackage[letterpaper]{geometry}
\usepackage{mathptmx}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{setspace}
\doublespacing

\usepackage{rotating}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{\thepage}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength\headsep{0.333in}

\newcommand{\bibent}{\noindent \hangindent 40pt}
\newenvironment{workscited}{\begin{center} Works Cited \end{center}}{\newpage }

\begin{document}
\begin{flushleft}

Bowen Zhao\
Professor\
Class\
\today\

\begin{center}
Title
\end{center}

\tableofcontents
\clearpage
\section{Background}
The history and development of Artificial Intelligence (AI) have revolutionized the digital landscape, fueling its rise to prominence in the contemporary era. The deep dive into AI's background, historical evolution, current development trends, and the reasons for its skyrocketing popularity elucidates our understanding of this game-changing technology.

\subsection{What is AI?}
Artificial Intelligence (AI) is a branch of computer science that aims to imbue machines with capabilities to mimic human intelligence. This broad and fascinating concept covers areas such as learning, reasoning, problem-solving, perception, and language understanding.

The inception of AI as a formal academic discipline occurred in 1956 during the Dartmouth Conference. However, the concept was present even earlier, with stories of artificial beings demonstrating intelligence dating back to Greek mythology.

Initially, AI researchers focused on creating symbolic methods, attempting to explicitly program all of the knowledge that an intelligent agent would need. This "Good Old-Fashioned AI" (GOFAI), as it is sometimes referred to, led to important developments in areas such as expert systems and game-playing AI (like the chess-playing Deep Blue).

However, it eventually became clear that encoding all of the world's knowledge in a machine-readable format was a herculean task. Thus, a shift towards machine learning began in the 1990s, with the goal of developing systems that could learn from data and improve with experience. The advent of the internet and the subsequent data explosion offered the perfect environment for machine learning algorithms to evolve and thrive.
\begin{workscited}


\end{workscited}

\end{flushleft}
\end{document}